\section{A Taxonomy of Robot-Learning Techniques}
\label{sec:taxonomy}

Figure~\ref{fig:taxonomy_main} organises the field into six branches. The dividing
question is \emph{what ships}: frozen weights (\S\ref{sec:vla}) or executable skills
(\S\ref{sec:code}). We tag mechanisms by \textbf{F}eedback, \textbf{S}earch, and
\textbf{M}emory throughout.

Table~\ref{tab:compare_main} compares all systems in the map on what each \emph{ships}, where
it is evaluated, and whether it improves from its own experience.
\input{tables/tab_compare_main}

\subsection{Survey methodology: building and partitioning the corpus}
\label{sec:method}

Figure~\ref{fig:prisma} summarises the corpus construction in the PRISMA~2020
style~\citep{prisma2020}. The corpus was assembled in two passes over a January~2016 to
July~2026 window. First, the 77 taxonomy systems were curated by \emph{seeding and
snowballing}: for each of the six branches we started from its landmark systems and chased
citations forward and backward until new candidates stopped appearing. Second, the 225-work
landscape corpus (Table~\ref{tab:landscape}) was gathered by five \emph{structured web-search
sweeps}, one per area cluster: (i) generalist and vision-language-action policies, imitation
and diffusion policies; (ii) language-model planning, task-and-motion planning, reward and data
synthesis; (iii) skill discovery, hierarchical reinforcement learning, and world models;
(iv) manipulation, dexterity, sim-to-real, locomotion, and benchmarks; and (v) representation
learning, offline reinforcement learning, navigation, and tactile sensing. Each sweep queried
the open web with area-specific search strings of the form ``\emph{<system or family name>
robot learning arXiv}'' and ``\emph{<area> survey/benchmark/dataset}'' over arXiv, the ACM
Digital Library, IEEE Xplore, Google Scholar, and venue proceedings pages (CoRL, RSS, ICRA,
IROS, NeurIPS, ICML, ICLR, CVPR).

\emph{Inclusion} required a work to (a) concern how an embodied agent's skill or policy is
authored, learned, transferred, evaluated, or distributed, and (b) carry verifiable metadata:
exact title, first author, year, and an arXiv identifier or DOI, each confirmed against the
source. \emph{Exclusion} removed pure perception, navigation, and locomotion work with no
bearing on skill authoring (retained only in the landscape appendix where it anchors an area),
works whose metadata could not be verified, and duplicates, detected by both bibliographic key
and arXiv identifier. Every reference in this survey passed the verification step; candidates
that failed it were discarded at harvest time, and we report that their count was not logged
rather than estimate it. Included systems were then mapped onto the taxonomy of
Figure~\ref{fig:taxonomy_main} by the mechanism definitions of Table~\ref{tab:defs}.

\paragraph{Placement: why a system enters the taxonomy or the landscape.}
Corpus membership and placement \emph{within} the corpus are two separate decisions, and it is the
second that produces the 77/225 split. A verified work is \emph{taxonomised}, that is, promoted to
the 77 systems of Figure~\ref{fig:taxonomy_main} and scored on all six axes of
Tables~\ref{tab:compare_main}--\ref{tab:compare_34}, only when it passes three tests.
(i)~\textbf{Axis-placeable}: it takes an unambiguous position on the weights-versus-skills question
and, for skill-authoring systems, on the self-improvement ladder of \S\ref{sec:code}, so that its
branch is determined rather than argued. (ii)~\textbf{Distinct}: it contributes a mechanism, rung,
or branch exemplar not already carried by a system in the map, rather than a near-variant, ablation,
or reimplementation of one. (iii)~\textbf{Fully characterisable}: its primary source reports enough
of what it \emph{ships}, how it learns, where it is evaluated, and whether it self-improves to fill
every comparison column without inference. A verified work that fails any one test is kept rather
than dropped: it stays in the landscape appendix (Table~\ref{tab:landscape}) as coverage evidence,
which is where precursors, same-point variants, and the supporting datasets, benchmarks, and
simulators live. Two further rules keep the map legible on a single page. First, when several
systems make the same taxonomic point, we taxonomise the earliest or most load-bearing landmark and
catalogue the rest in the landscape. Second, pure perception, navigation, or locomotion work is
taxonomised only when it directly authors or improves a manipulation skill, and otherwise anchors
its area in the landscape alone. The 77/225 split is therefore a statement about analytical
\emph{role}, sharp exemplar versus representative breadth, not about a work's quality or importance.

\input{figures/fig_prisma}

\subsection{The corpus at a glance}
\label{sec:corpus_gallery}

Figure~\ref{fig:corpus_overview} summarises the whole corpus at a glance, and
Figure~\ref{fig:corpus_dist} profiles the 225 landscape works (Table~\ref{tab:landscape},
Appendix~\ref{sec:landscape}) by publication year, evaluation domain, learning signal, and
embodiment; every count is the exact tally of that table. Figure~\ref{fig:pole_trend} then charts the
two poles of Figure~\ref{fig:corpus_collage} by year of release, showing both paradigms emerging only
recently, with code-as-policy the larger and faster-growing pole.

Figures~\ref{fig:robots_canvas} and~\ref{fig:plots_canvas} then give a visual overview of the surveyed
systems: the real and simulated robots they run on (Figure~\ref{fig:robots_canvas}) and the empirical
results they report (Figure~\ref{fig:plots_canvas}); the two poles of the opening thesis figure
(Figure~\ref{fig:corpus_collage}) recur here across every embodiment. Every panel is a live hyperlink
to its source paper and is cropped from a specific figure of it; Table~\ref{tab:canvas_provenance}
records the source paper and the figure number for each, so that no image is used without a
traceable, clickable origin. The figures are vector graphics with the photographs embedded at full
resolution, so they can be zoomed without pixelation.

\input{figures/fig_corpus_overview}
\input{figures/fig_corpus_dist}
\input{figures/fig_pole_trend}
\input{figures/fig_robots_canvas}
\input{figures/fig_plots_canvas}
