\subsection{Skill Libraries: How a Repertoire is Built}
\label{sec:skill}

Where \S\ref{sec:code} asked \emph{how} a code skill improves, this family asks the prior
question of \emph{how a repertoire of skills is built at all}. The \S3.4 branch of
Figure~\ref{fig:taxonomy_main} organises these systems along one axis, skills learned as latent reinforcement-learning policies
versus skills stored as retrievable code, and only the code flavour self-improves without
gradients, which links this family back to \S\ref{sec:code}.

Before surveying these systems we note that the word ``skill'' is badly overloaded.
Table~\ref{tab:skill_senses} separates five senses that the literature routinely conflates,
from a latent policy to a market product, and records which properties each sense affords.

\input{tables/tab_skill_senses}

\subsubsection{Unsupervised and latent skill discovery}
The oldest lineage learns a diverse set of skills with \emph{no task reward and no code}, by
maximising an information-theoretic objective. \emph{DIAYN}~\citep{diayn} maximises the mutual
information between a latent skill code and the visited states, yielding distinguishable
behaviours; \emph{DADS}~\citep{dads} makes the discovered skills dynamics-aware and hence
usable for model-based control; and \emph{LSD}~\citep{lsd}, \emph{CIC}~\citep{cic}, and
\emph{METRA}~\citep{metra} push toward more dynamic, far-reaching, and scalable skills through
Lipschitz constraints, contrastive objectives, and metric-aware abstractions respectively.

\subsubsection{Skill-based and hierarchical reinforcement learning}
A second lineage extracts a continuous \emph{skill space} from offline data and then plans or
learns within it. \emph{SPiRL}~\citep{spirl} learns a skill embedding together with a skill
prior that accelerates downstream RL; \emph{OPAL}~\citep{opal} discovers temporally extended
primitives for offline RL; \emph{PARROT}~\citep{parrot} learns an invertible behavioural
prior; and \emph{SkiMo}~\citep{skimo} learns a skill dynamics model so that planning happens
directly in skill space.

\subsubsection{LLM and code skill libraries}
The code flavour, where the self-improving methods of \S\ref{sec:code} live, stores skills as
retrievable programs. \emph{Voyager}~\citep{voyager} curates an ever-growing library of
verified code skills in Minecraft; \emph{LOTUS}~\citep{lotus} performs continual imitation
learning through unsupervised skill discovery; \emph{LRLL}~\citep{lrll} bootstraps a composable
robot library with language models; and \emph{BOSS}~\citep{boss} and \emph{SPRINT}~\citep{sprint}
grow skill repertoires by LLM-guided bootstrapping and instruction relabelling. The most recent
entries close the loop between video and code: \emph{Uni-Skill}~\citep{uniskill} builds a
self-evolving skill repository from unstructured robot video, and \emph{SkillFlow}~\citep{skillflow}
benchmarks lifelong discovery, patching, and reuse of a skill library.

\subsubsection{Open-world LLM-agent libraries}
Finally, embodied LLM agents accumulate skills from open-ended experience.
\emph{GITM}~\citep{gitm} and \emph{JARVIS-1}~\citep{jarvis1} pair a planner with text or
multimodal memory in Minecraft; \emph{ExpeL}~\citep{expel} extracts reusable insights from a
stream of trials; \emph{Optimus-1}~\citep{optimus1} adds a hybrid multimodal memory for
long-horizon tasks; and \emph{Odyssey}~\citep{odyssey} equips an agent with an open-world
library of primitive and compositional skills. These systems foreshadow the marketplace
dynamics of \S\ref{sec:open}: a library that grows with use.

Table~\ref{tab:compare_34} contrasts the four sub-families on skill form, whether they are
gradient-trained or LLM-authored, whether they keep a persistent library, and their domain.
\input{tables/tab_compare_34}
